Biomass allocation, plant functional types and leaf area vs. mass

### 2014-08-06 manuscript/draftpaper.tex
added better SLA - pipe model figures, and glopnet data

>>>>

\section{Results}
(this will not be separate in the manuscript, just temporary notes here)

Figure (figure\_mlfastbh\_sla\_pft.pdf) shows that across plant functional types (pfts) (but not within pfts), the ratio of leaf mass to stem cross-sectional area is negatively correlated with specific leaf area. This means that pfts with larger SLA display less leaf mass per unit stem area (and hence per unit aboveground biomass), in a way so that leaf area per stem cross sectional area does not differ by pft (figure\_alfastbh\_sla\_pft.pdf). The convergent trait, independent of plant functional type, is then the ratio of leaf area to stem area.

Though leaf area per stem area did not differ between pfts (figure\_alfastbh\_sla\_pft and other figure tba), within pfts it was correlated to sla. In other words, for a given pft, species with higher sla tended to have larger total leaf area at a given stem cross-sectional area. This was in a way so that leaf mass per unit stem area did not correlate to sla within a pft, so that within pfts the more convergent trait is in fact leaf mass per unit stem area.

The implication for global vegetation models that use pft as the unit of parameterization is that specific leaf area (pft-specific) should be combined with a target leaf area to stem area ratio to give a leaf mass fraction that constrains the allocation of carbon. This is what LPJ does, but there the pipe model ratio is actually pft-specific (and nobody knows where it comes from; see sitch and also Hickler).

Fixed allocation fraction models would get the distribution of biomass right if leaf turnover rate is exactly proportional to specific leaf area (because if an extra unit of leaf area is produced when SLA is increased, this could be offset exactly by a faster turnover rate). However glopnet says that turnover rate scales with more than SLA (exponent 1.3, but not a great fit).
